Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-27 paper_jar/paper.tex
Add comments based on notebook "bonus_results"
Quick comparison of figures and plots in notebook with paper.
Revise paper

We evaluated our approach using the SAT Competition~2022 Anniversary Track dataset~\cite{sat2022}, consisting of 5355~instances and runtimes of 28~solvers.
Cross-validation was performed by treating each solver as the new solver once and learning to predict its PAR-2 rank.
On average, our predictions achieve a ranking accuracy of approximately \SI{92}{\%} with only approximately \SI{10}{\%} of the runtime required to evaluate these solvers on the complete set of instances.
Our entire source code\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}} and experimental data\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking-data}} are available on GitHub.
%JB: data repo not updated since TACAS; does it also contain all the results for the new experiments? as a minimum, it should mention the journal version of the paper (see README of code repo)
%JB: code repo currently has all JAR changes in a branch; probably best to push these changes to "main" for review (in case reviewers have a look at repo but don't switch branches)

@@

  $\mathcal{M} \leftarrow \operatorname{initModel}\left(\mathcal{A},\, \mathcal{I},\, r,\, \hat{a}\right)$ \tcp*{cf. Section~\ref{sec:main:model}}
  %JB: do we actually need \hat{a} here? (does not provide any information we could store/use here)

@@

The model $M$ provides a prediction function $f : \mathcal{\hat A} \times \mathcal{I} \rightarrow \mathbb{R}$ for all solvers $\mathcal{\hat A} := \mathcal{A} \cup \lbrace \hat a \rbrace$.
%JB: shouldn't we drop the algorithm as an argument (for $f$ and later for $f'$), since we only train and predict for one solver ($\hat{a}$) anyway? (what would the predictions for the other solvers be -- looking up the exact runtime values from $r$?); instead, could use $\hat{a}$ as a subscript of $f$
This prediction function powers instance selection as described in Section~\ref{sec:main:selection}.
In the update step (Algorithm~\ref{algALBenchmark},~Line~7), the model is trained to predict a transformed version of solver runtime (cf.~Section~\ref{sec:main:model:transformation}) for the new solver~$\hat{a}$, using the features described in Section~\ref{sec:exdesign:data} and the previously acquired runtimes~$\mathcal{R}$.
Each iteration trains a new prediction model from scratch since the time for running the solver~$\hat{a}$ on one instance~$e$ (Line~5) dominates the training time of the model~$M$ on all acquired instances~$\mathcal{R}$ by a significant margin.
Once the benchmarking loop terminates, the score of the new solver~$\hat{a}$ is predicted and then returned (Lines~8--9).

@@

Selecting an instance based on the prediction model is a core functionality of our framework (cf.~Algorithm~\ref{algALBenchmark}, Line~4).
In this section, we introduce two instance sampling strategies, one that minimizes uncertainty and one that maximizes information gain.
Both strategies use the model's prediction function~$f$ and are inspired by existing work on active learning~\cite{settles2009active}.
These methods require the model's predictions to include probabilities for the $k$ discrete runtime labels.
Let \mbox{$f' : \mathcal{\hat A} \times \mathcal{I} \rightarrow \left[0, 1\right]^k$} denote this modified prediction function.
In the following, the set $\tilde{\mathcal{I}} \subseteq \mathcal{I}$ denotes the instances that have already been sampled.

@@

The uncertainty sampling strategy selects the instance closest to the model's decision boundary.
This is achieved by selecting the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that minimizes the certainty~$U(e)$, which is specified by the following equation:
%
\begin{equation*}
  \operatorname{U}(e) := \left\lvert \frac{1}{k} - \max_{n \in \left\lbrace 1, \dots, k \right\rbrace} f'\!\left(\hat{a}, e\right)_{n} \right\rvert
\end{equation*}

@@

The information-gain sampling strategy selects the instance with the highest expected entropy reduction regarding the runtime labels.
To be more precise, we select the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that maximizes $IG(e)$, which is specified in the following equation:
%
\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f'(\hat{a}, e)_{n} \operatorname{\hat H}_n(e)
\end{equation*}
%
In the equation, $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ over all $a \in \mathcal{A}$ and $\operatorname{H}(e, n)$ denotes the entropy of these labels plus $n$ as the runtime label for $\hat{a}$.
The term $\operatorname{\hat H}_n(e)$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.
By maximizing the information gain, instances are selected that identify solvers with similar behavior.
%JB: "similar behavior" is a bit vague; strategy favors instances where the distribution of solvers over clusters is skewed rather than uniform, right? and the new solver only has little influence here, since its predicted labels is only one of |A| + 1 labels to determine entropy, right?

@@

The Wilcoxon stopping criterion terminates the active-learning process based on the confidence that the predicted runtime labels of the new solver are sufficiently different from those of existing solvers.
This criterion is loosely inspired by Matricon et~al.~\cite{MatriconAFSH21}.
To assess the statistical significance of the predicted runtime labels, the criterion uses the average $p$-value $W_{\hat{a}}$ of a Wilcoxon signed-rank test $\operatorname{w}(S,P)$ of the runtime label distributions ${S=\{ \gamma(a, e) \mid e \in \mathcal{I} \}}$ for an existing solver $a$ and \mbox{$P=\{ f(\hat a, e) \mid e \in \mathcal{I} \}$} of the new solver $\hat{a}$:
%
\begin{equation*}
  W_{\hat{a}} := \frac{1}{\lvert \mathcal{A} \rvert} \sum_{a \in \mathcal{A}} \operatorname{w}(S, P)
\end{equation*}
%
To improve the stability of this criterion and mitigate the impact of outliers, we employ an exponential moving average~$W^{(i)}_{\exp}$:
%
\begin{align*}
  W_{\exp}^{\left(0\right)} &:= 1\\
  W_{\exp}^{\left(i\right)} &:= \beta W_{\hat{a}} + \left(1 - \beta\right) W_{\exp}^{\left(i - 1\right)}
\end{align*}
%
Active learning terminates when the value of $W^{(i)}_{\exp}$ drops below a fixed threshold.

@@

  \BlankLine
  \tcp{Determine Ranking Accuracy}
    $O_{\operatorname{acc}} \leftarrow 0$ \;    
    \For{$a \in \mathcal{A}$}{
      %JB: mabye Lines 6 and 8 should use A' instead of A (at the moment, solver is also compared to itself but this does not increase ranking accuracy since second factor in Line 7 is 0)
      \If{$\bigl(s_k(a) - s_{\hat a}\bigr) \cdot \bigl(\operatorname{par_2}(a) - \operatorname{par_2}(\hat a)\bigr) > 0$}{
           $O_{\operatorname{acc}} \leftarrow O_{\operatorname{acc}} + \frac{1}{|\mathcal{A}|}$ \;
      }
    }

@@

In addition, we retrieve instance family information\footnote{\url{https://benchmark-database.de/getdatabase/meta_db}} to evaluate the composition of our sampled benchmarks.
Instance families consist of instances from the same application domain, such as planning, cryptography, etc., and are valuable for analyzing solver performance.
%
For hyperparameter tuning, we randomly sample \SI{10}{\%} of the complete set of 5355 instances with stratification regarding the instance family.
All instance families that are too \emph{small}, i.e., \SI{10}{\%} of them correspond to less than one instance, are put into one meta-family for stratification.
%JB: i.e., families with less than 10 instances? could be phrased more directly
This \emph{tuning dataset} allows a more extensive exploration of the hyperparameter space.

@@

We experiment with the following instantiations of the instance \emph{selection} (cf. Section~\ref{sec:main:selection}).
Since the potential runtime of the solver experiments is orders of magnitude larger than the model update time, we increment our benchmark one instance at a time rather than using batches of multiple instances, which is also proposed in recent advances in active learning~\cite{SinhaED19,2019gaal}.
%JB: not entirely clear if one-at-a-time "is also propsed" or batching "is also proposed"
A drawback of this is the lack of parallel execution of runtime experiments.

\begin{itemize}\setlength{\itemsep}{1pt}
  \item Random sampling 
  \item Uncertainty sampling
  \vspace*{-1ex}
  \begin{itemize}\setlength{\itemsep}{1pt}
    \item Fallback threshold: Use random sampling for the first \SI{0}{\%}, \SI{5}{\%}, \SI{10}{\%}, \SI{15}{\%}, or \SI{20}{\%} of instances to explore the instance space.
    \item Runtime scaling: Whether to normalize uncertainty scores per instance by the average runtime of solvers on it or use the absolute values.
    %JB: but isn't the uncertainty score a difference of probabilities rather than directly runtime-related anyway? so probably not a normalization in the strict sense (maybe use term "divide" instead)
  \end{itemize}

@@

To define this prediction target, we partition the solver runtimes into $k$~clusters.
We conduct this clustering step per instance, i.e., the solvers forming a particular cluster may differ from instance to instance.
The adapted solver scoring function~$s_k$ (cf.~Equation~\eqref{eq:rankingeq}) subsequently uses the cluster labels.
In preliminary experiments, the most \emph{useful} labels were produced with hierarchical clustering and a log-single-linkage criterion; we will discuss our notion of label usefulness later.
Other clustering approaches we have tried include hierarchical clustering with mean-, median-, and full-linkage criteria, as well as $k$-means and spectral clustering.
%JB: What is "full" -- "complete"?

@@

% TODO tfu: Amount of significant solver pairs (Wilcoxon signed-rank, 5% alpha), 
% Amount of significant pairs:
% PAR-2:   684/756 = 0.9048
% timeout: 660/756 = 0.8730
% k=3:     662/756 = 0.8757
% k=4:     662/756 = 0.8757
% k=5:     662/756 = 0.8757
\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/par2sigdiff.pdf}
		\caption{PAR-2 scores.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/timeoutsigdiff.pdf}
		\caption{Timeouts.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/s3sigdiff.pdf}
		\caption{$s_3$ scores.}
	\end{subfigure}
	\caption{Solver pairs with significant differences regarding their scorings are colored white, non-significant ones black. Solvers are ordered identically to Table~\ref{tab:ranking}.}
	\label{fig:solver-confusion-matrices}
\end{figure}

We also analyze how runtime discretization affects the distinguishability of solver pairs.
The matrices in Fig.~\ref{fig:solver-confusion-matrices} visualize which solver pairs exhibit significant differences in their PAR-2 scores, timeouts, and $s_3$ scores.
According to a Wilcoxon signed-rank test with a significance level of $\alpha = 0.05$, \SI{87.83}{\%} of the solver pairs have significantly different scores after discretization, which is only a slight decrease compared to \SI{89.95}{\%} before discretization.
%JB: numbers in notebook "bonus_results" differ
%JB: does "after discretization" mean s_3 or timeout? and what is then the number for the other one?
These results support the usefulness of discretized runtimes for our active learning framework.

@@

A static benchmark utilizing the most frequently AL-sampled instances exhibits suboptimal performance compared to active learning and random sampling.
This outcome is anticipated since the static benchmark fails to reflect an appropriate balance of instance families.
For example, families whose instances are uniformly randomly selected by AL, e.g., for different solvers, appear less frequently in this benchmark than families where some instances are sampled more often than others.
% MI: What? I don't understand this sentence.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.6\textwidth]{../plots/instoccs.pdf}
  \caption{Frequency with which individual problem instances are selected within all active-learning benchmarks. Instances that are chosen more frequently are intuitively more important for distinguishing solver runtimes.}
  \label{fig:instoccs}
\end{figure}

\begin{figure}[tb]
  \centering
  \resizebox{0.85\textwidth}{!}{
    \graphicspath{{../plots/}}
    \input{../plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples.
  }
  \label{fig:annifinalfamilies}
\end{figure}

Fig.~\ref{fig:instoccs} illustrates the frequency distribution with which individual instances are selected across all active learning benchmarks.
%JB: on the full dataset, I suppose (since tuning dataset does not contain all instances)? and what is "all" aggregating over? these information may also go into the figure's caption
A small proportion of instances is selected with great frequency, while most instances are selected on only a few occasions.
This indicates that there is no fixed subset of instances that can perfectly distinguish all solvers, which highlights the value of employing an active-learning-based strategy.
%JB: could also indicate that (1) there is such a set but AL cannot always find it or (2) there are multiple such sets and different AL runs return different sets

>>>>

We evaluated our approach using the SAT Competition~2022 Anniversary Track dataset~\cite{sat2022}, consisting of 5355~instances and runtimes of 28~solvers.
Cross-validation was performed by treating each solver as the new solver once and learning to predict its PAR-2 rank.
On average, our predictions achieve a ranking accuracy of approximately \SI{92}{\%} with only approximately \SI{10}{\%} of the runtime required to evaluate these solvers on the complete set of instances.
Our entire source code\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}} and experimental data\footnote{\url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking-data}} are available on GitHub.

@@

  $\mathcal{M} \leftarrow \operatorname{initModel}\left(\mathcal{A},\, \mathcal{I},\, r\right)$ \tcp*{cf. Section~\ref{sec:main:model}}

@@

The model $M$ provides a prediction function $f_{\hat a} : \mathcal{I} \rightarrow \mathbb{R}$ for solver $\hat a$.
This prediction function powers instance selection as described in Section~\ref{sec:main:selection}.
In the update step (Algorithm~\ref{algALBenchmark},~Line~7), the model is trained to predict a transformed version of solver runtime (cf.~Section~\ref{sec:main:model:transformation}) for the new solver~$\hat{a}$, using the features described in Section~\ref{sec:exdesign:data} and the previously acquired runtimes~$\mathcal{R}$.
Each iteration trains a new prediction model from scratch since the time for running the solver~$\hat{a}$ on one instance~$e$ (Line~5) dominates the training time of the model~$M$ on all acquired instances~$\mathcal{R}$ by a significant margin.
Once the benchmarking loop terminates, the score of the new solver~$\hat{a}$ is predicted and then returned (Lines~8--9).

@@

Selecting an instance based on the prediction model is a core functionality of our framework (cf.~Algorithm~\ref{algALBenchmark}, Line~4).
In this section, we introduce two instance sampling strategies, one that minimizes uncertainty and one that maximizes information gain.
Both strategies use the model's prediction function~$f$ and are inspired by existing work on active learning~\cite{settles2009active}.
These methods require the model's predictions to include probabilities for the $k$ discrete runtime labels.
Let $f_{\hat a}' : \mathcal{I} \rightarrow \left[0, 1\right]^k$ denote this modified prediction function.
In the following, the set $\tilde{\mathcal{I}} \subseteq \mathcal{I}$ denotes the instances that have already been sampled.

@@

The uncertainty sampling strategy selects the instance closest to the model's decision boundary.
This is achieved by selecting the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that minimizes the certainty~$U(e)$, which is specified by the following equation:
%
\begin{equation*}
  \operatorname{U}(e) := \left\lvert \frac{1}{k} - \max_{n \in \left\lbrace 1, \dots, k \right\rbrace} f_{\hat{a}}'(e)_{n} \right\rvert
\end{equation*}

@@

The information-gain sampling strategy selects the instance with the highest expected entropy reduction regarding the runtime labels.
To be more precise, we select the instance $e \in \mathcal{I} \setminus \tilde{\mathcal{I}}$ that maximizes $IG(e)$, which is specified in the following equation:
%
\begin{equation*}
  \operatorname{IG}(e) := \operatorname{H}(e) - \sum_{n = 1}^{k} f_{\hat{a}}'(e)_{n} \operatorname{\hat H}(e)_n
\end{equation*}
%
In the equation, $\operatorname{H}(e)$ denotes the entropy of the runtime labels $\gamma(a, e)$ over all $a \in \mathcal{A}$ and $\operatorname{\hat H}(e)$ denotes the entropy of these labels plus the runtime label for $\hat{a}$.
The term $\operatorname{\hat H}(e)_n$ is computed for every possible runtime label $n \in \{1, \dots, k\}$.
By maximizing the information gain, instances are selected that identify solvers with similar runtime cluster labels, i.e., the new solver ranks similarly to the solvers in the same clusters.

@@

The Wilcoxon stopping criterion terminates the active-learning process based on the confidence that the predicted runtime labels of the new solver are sufficiently different from those of existing solvers.
This criterion is loosely inspired by Matricon et~al.~\cite{MatriconAFSH21}.
To assess the statistical significance of the predicted runtime labels, the criterion uses the average $p$-value $W_{\hat{a}}$ of a Wilcoxon signed-rank test $\operatorname{w}(S,P)$ of the runtime label distributions ${S=\{ \gamma(a, e) \mid e \in \mathcal{I} \}}$ for an existing solver $a$ and \mbox{$P=\{ f_{\hat a}(e) \mid e \in \mathcal{I} \}$} of the new solver $\hat{a}$:
%
\begin{equation*}
  W_{\hat{a}} := \frac{1}{\lvert \mathcal{A} \rvert} \sum_{a \in \mathcal{A}} \operatorname{w}(S, P)
\end{equation*}
%
To improve the stability of this criterion and mitigate the impact of outliers, we employ an exponential moving average~$W^{(i)}_{\exp}$:
%
\begin{align*}
  W_{\exp}^{\left(0\right)} &:= 1\\
  W_{\exp}^{\left(i\right)} &:= \beta W_{\hat{a}} + \left(1 - \beta\right) W_{\exp}^{\left(i - 1\right)}
\end{align*}
%
Active learning terminates when the value of $W^{(i)}_{\exp}$ drops below a fixed threshold.

@@

  \BlankLine
  \tcp{Determine Ranking Accuracy}
    $O_{\operatorname{acc}} \leftarrow 0$ \;    
    \For{$a \in \mathcal{A}'$}{
      \If{$\bigl(s_k(a) - s_{\hat a}\bigr) \cdot \bigl(\operatorname{par_2}(a) - \operatorname{par_2}(\hat a)\bigr) > 0$}{
           $O_{\operatorname{acc}} \leftarrow O_{\operatorname{acc}} + \frac{1}{|\mathcal{A}'|}$ \;
      }
    }

@@

In addition, we retrieve instance family information\footnote{\url{https://benchmark-database.de/getdatabase/meta_db}} to evaluate the composition of our sampled benchmarks.
Instance families consist of instances from the same application domain, such as planning, cryptography, etc., and are valuable for analyzing solver performance.
%
For hyperparameter tuning, we randomly sample \SI{10}{\%} of the complete set of 5355 instances with stratification regarding the instance family.
All instance families that are too \emph{small}, i.e., families with less than 10 instances, are put into one meta-family for stratification.
This \emph{tuning dataset} allows a more extensive exploration of the hyperparameter space.

@@

We experiment with the following instantiations of the instance \emph{selection} (cf. Section~\ref{sec:main:selection}).
Since the potential runtime of the solver experiments is orders of magnitude larger than the model update time, we increment our benchmark one instance at a time rather than using batches of multiple instances.
Both are used in the state-of-the-art in active learning~\cite{SinhaED19,2019gaal}.
A drawback of this is the lack of parallel execution of runtime experiments.

\begin{itemize}\setlength{\itemsep}{1pt}
  \item Random sampling 
  \item Uncertainty sampling
  \vspace*{-1ex}
  \begin{itemize}\setlength{\itemsep}{1pt}
    \item Fallback threshold: Use random sampling for the first \SI{0}{\%}, \SI{5}{\%}, \SI{10}{\%}, \SI{15}{\%}, or \SI{20}{\%} of instances to explore the instance space.
    \item Runtime scaling: Whether to scale the uncertainty scores by the average runtime of solvers or use $\operatorname{U}(e)$ as is.
  \end{itemize}

@@

To define this prediction target, we partition the solver runtimes into $k$~clusters.
We conduct this clustering step per instance, i.e., the solvers forming a particular cluster may differ from instance to instance.
The adapted solver scoring function~$s_k$ (cf.~Equation~\eqref{eq:rankingeq}) subsequently uses the cluster labels.
In preliminary experiments, the most \emph{useful} labels were produced with hierarchical clustering and a log-single-linkage criterion; we will discuss our notion of label usefulness later.
Other clustering approaches we have tried include hierarchical clustering with mean-, median-, and complete-linkage criteria, as well as $k$-means and spectral clustering.

@@

% Amount of significant solver pairs (Wilcoxon signed-rank, 5% alpha):
% PAR-2:   684/756 = 0.9048
% timeout: 660/756 = 0.8730
% k=3:     662/756 = 0.8757
% k=4:     662/756 = 0.8757
% k=5:     662/756 = 0.8757
\begin{figure}[tb]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/par2sigdiff.pdf}
		\caption{PAR-2 scores.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/timeoutsigdiff.pdf}
		\caption{Timeouts.}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[width=3.9cm]{../plots/s3sigdiff.pdf}
		\caption{$s_3$ scores.}
	\end{subfigure}
	\caption{Solver pairs with significant differences regarding their scorings are colored white, non-significant ones black. Solvers are ordered identically to Table~\ref{tab:ranking}.}
	\label{fig:solver-confusion-matrices}
\end{figure}

We also analyze how runtime discretization affects the distinguishability of solver pairs.
The matrices in Fig.~\ref{fig:solver-confusion-matrices} visualize which solver pairs exhibit significant differences in their PAR-2 scores, timeouts, and $s_3$ scores.
According to a Wilcoxon signed-rank test with a significance level of $\alpha = 0.05$, \SI{87.57}{\%} of the solver pairs have significantly different scores after $\gamma_3$-discretization, which is only a slight decrease compared to \SI{90.48}{\%} before discretization.
$\gamma_2$-discretization significantly distinguishes \SI{87.30}{\%} of solver pairs.
These results support the usefulness of discretized runtimes for our active learning framework.

@@

A static benchmark utilizing the most frequently AL-sampled instances exhibits suboptimal performance compared to active learning and random sampling.
This outcome is anticipated since the static benchmark fails to reflect an appropriate balance of instance families.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.6\textwidth]{../plots/instoccs.pdf}
  \caption{Frequency with which individual problem instances are selected within all active-learning benchmarks. Instances that are chosen more frequently are intuitively more important for distinguishing solver runtimes. Results are on the full dataset with cross-validation over all solvers.}
  \label{fig:instoccs}
\end{figure}

\begin{figure}[tb]
  \centering
  \resizebox{0.85\textwidth}{!}{
    \graphicspath{{../plots/}}
    \input{../plots/anni_final_families.pgf}
  }
  \caption{
    Scatter plot illustrating the relative importance of different instance families for ranking on the full dataset. The x-axis depicts the frequency of instance families in the dataset, while the y-axis represents the average frequency in the samples selected by active learning. The dashed line represents families that occur with the same frequency in the dataset and samples. Results are on the full dataset with cross-validation over all solvers.
  }
  \label{fig:annifinalfamilies}
\end{figure}

Fig.~\ref{fig:instoccs} illustrates the frequency distribution with which individual instances are selected across all active learning benchmarks regarding the full dataset with cross-validation over all solvers.
A small proportion of instances is selected with great frequency, while most instances are selected on only a few occasions.
This indicates that there is no fixed subset of instances that can perfectly distinguish all solvers, which highlights the value of employing an active-learning-based strategy.
